DisCon Kids Pilot

### 2018-08-29 analysis/01_kids.Rmd
preload audios

files <- dir("../../data/kids_pilot/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../data/kids_pilot/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$data$data)
  raw_data <- bind_rows(raw_data, id)
}

>>>>

files <- dir("../../kids_simple/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../kids_simple/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$data$data)
  raw_data <- bind_rows(raw_data, id)
}
